Subject-specific curves for time series forecasting of smart meter demand

### 2020-03-29 sscts-paper-1-wp.Rmd
Fix one day ahead forecast figure. Focus on SSC model as it performs best.

(ref:one-day-ahead-forecast-cap) One-day ahead forecasts for `r format(p_one_day_ahead_date, "%e %B, %Y")`. The dashed black line shows the actual observed values for this day. The INS models often show erratic jumps due to overfitting.

```{r one-day-ahead-forecast, fig.cap="(ref:one-day-ahead-forecast-cap)"}
model_df %>%
  filter(fcst_date == p_one_day_ahead_date) %>%
  unnest(cols = c(preds)) %>%
  # filter(bid %in% sample(unique(bid), 3),
  #        fcst_date %in% (dmy("13/3/2017")+0:4)) %>%
  filter(bid %in% sample(unique(bid), 6),
         model %in% c("Naive", "INS", "SSC")) %>%
  mutate(ts = as_datetime(fcst_date) + minutes((period - 1) * 24 * 60 / 96)) %>%
  ggplot(aes(x = ts)) +
  geom_line(aes(y = wh), colour = "black", linetype = "dashed") +
  geom_line(aes(y = pred, colour = model), alpha = 0.7) +
  facet_wrap(~bid, ncol = 2, scales = "free_y") +
  labs(
    y = expression(Normalised ~ electricity ~ (Wh / m^2)),
    x = "Date",
    colour = "Model"
  ) +
  scale_x_datetime(date_labels = "%H:%M") +
  theme(legend.position = "bottom")
```

>>>>

(ref:one-day-ahead-forecast-cap) One-day ahead forecasts for `r format(p_one_day_ahead_date, "%e %B, %Y")`. The Naive (yesterday's actuals) and SSC models are shown. The naive model often includes erratic spikes whereas the SSC model tends to produce a smoother profile.

```{r one-day-ahead-forecast, fig.cap="(ref:one-day-ahead-forecast-cap)"}
p_bid <- paste0("BID", c("0025", "0058", "0112", "0203", "0205", "1101"))

model_df %>%
  filter(fcst_date == p_one_day_ahead_date) %>%
  unnest(cols = c(preds)) %>%
  filter(bid %in% p_bid,
         model %in% c("Naive", "SSC")) %>%
  mutate(ts = as_datetime(fcst_date) + minutes((period - 1) * 24 * 60 / 96)) %>%
  select(ts, model, Actual = wh, pred, bid) %>% 
  pivot_wider(names_from = model, values_from = pred) %>% 
  pivot_longer(cols = c(Actual, Naive, SSC)) %>% 
  ggplot(aes(x = ts)) +
  geom_line(aes(y = value, colour = name)) +
  facet_wrap(~bid, ncol = 2, scales = "free_y") +
  labs(
    y = expression(Normalised ~ electricity ~ (Wh / m^2)),
    x = "Date",
    colour = "Model"
  ) +
  scale_colour_manual(values = c("black", "grey", ba_palette[2])) +
  scale_x_datetime(date_labels = "%H:%M") +
  theme(legend.position = "bottom")
```
